---
title: "PDFRpoert"
author: "my_name"
date: "2023-08-25"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#load libraries 

```{r, message=FALSE,warning=FALSE}
library(tidyverse)
library(knitr)
library(corrplot)
#library(kableExtra)
```

# load data 

```{r}
space<- read_csv("SPACE_wide_2022.csv")
space[space==999998] <- NA
```

# Data preparatio
```{r}
df<- space %>%
  select(AGE, D1, EDUCATION, D6_1, D6_2A, D6_2B, HHSIZE, DEPCHILDREN, INCOME,COUNTRY,
         QQ1A_1,,QQ1A_2,QQ1A_3,QQ1D,
         starts_with(c("QA5A_", "QA6A_","QA7A_","QA7AI_", "QA7AII_","QA8A_", "QA8AI_1")))%>%
  mutate(AGE=case_when(AGE==1~"18-24",
                       AGE==2~"25-29",
                       AGE==3~"30-34",
                       AGE==4~"35-39",
                       AGE==5~"40-44",
                       AGE==6~"45-49",
                       AGE==7~"50-54",
                       AGE==8~"55-59",
                       AGE==9~"60-64",
                       AGE==10~"64-69",
                       AGE==11~"70-74",
                       AGE==12~"75+"),
         D1=case_when(D1==1~'Male',
                      D1==2~"Female",
                      D1==3~"Other, non-binary"),
         EDUCATION= case_when(EDUCATION==1~"Primary/lower secondary education",
                              EDUCATION==2~"Upper/post-secondary education",
                              EDUCATION==3 ~"University/PhD/research",
                              EDUCATION=='=999998'~"Refusal / No answer"),
         D6_1= case_when(D6_1==1~"Self-employed",
                         D6_1==2~"Employee",
                         D6_1==3~"Without a professional activity or student",
                         D6_1=="999998"~"Refusal / No answer"),
         D6_2A= case_when(D6_2A==1~"General management, director or top management",
                          D6_2A==2~"Middle management or other management (e.g. department head)",
                          D6_2A==3~"Employed professional (e.g. doctor, lawyer, accountant, architect)",
                          D6_2A==4~"Employed position, working mainly at a desk",
                          D6_2A==5~"Employed position, not at a desk",
                          D6_2A==6~"Manual worker",
                          D6_2A==7~"Other employee",
                          D6_2A==999998~"Refusal / No answer"),
         D6_2B= case_when(D6_2B==1~	"Responsible for housework (e.g. ordinary shopping, looking after home and family)",
                          D6_2B==2~	"Student (full-time)",
                          D6_2B==3~	"Unemployed or temporarily not working",
                          D6_2B==4~	"Retired or unable to work through illness",
                          D6_2B==5~	"Other",
                          D6_2B==999998~	"Refusal / No answer"),
         INCOME= case_when(INCOME==1~	"EUR 750 or less",
                           INCOME==2~	"Between EUR 751 and EUR 1,500",
                           INCOME==3~	"Between EUR 1,501 and EUR 2,500",
                           INCOME==4~"Between EUR 2,501 and EUR 4,000",
                           INCOME==5~	"More than EUR 4,000",
                           INCOME==999998~	"Refusal")
         
  )
```

# Correlation for Demographic
```{r}
### correlation ####
df_cor<- space %>%
  select(AGE, D1, EDUCATION, D6_1, D6_2A, D6_2B, HHSIZE, DEPCHILDREN, INCOME)

df_cor[df_cor>100]<- NA

cor_mat<-cor(df_cor,use='pairwise.complete.obs')
```

```{r fig.cap ="Correlation Matrix",fig.width=12, fig.height=8}
corrplot(cor_mat, method = 'number',col = COL2('RdYlBu', 2),
         type = 'lower', tl.col='black')
```

The correlation matrix depicts the relationships between various variables. Notable correlations include a moderate positive relationship between AGE and D6_2B (0.5399) and a strong positive relationship between HHSIZE and DEPCHILDREN (0.7473), suggesting larger households tend to have more dependent children. There's a moderate negative correlation between DEPCHILDREN and both AGE (-0.3418) and HHSIZE (-0.3834), implying that as the number of dependent children increases, household size and the age of respondents tend to decrease. Education shows a strong negative correlation with D6_2A (-0.3705), suggesting that higher education levels are associated with less agreement with a particular statement (D6_2A). Additionally, D1 exhibits a moderate negative correlation with D6_2B (-0.2106), implying that as the level of agreement with D1 increases, agreement with D6_2B tends to decrease. However, some correlations, like D6_1 with D6_2A and D6_2B, have missing values, indicating a lack of correlation data for these pairs.

# Visualization of the variables  

```{r}

ggplot(df, aes(AGE)) + 
  geom_bar(aes(y = (..count..)/sum(..count..)), fill="blue", color="black") + 
  scale_y_continuous(labels=scales::percent) +
  labs(y = "Percent", title = "Age Distribution in %")+
  theme_classic()

#The plot shows that most of the people who took part in the
# survey falls between 64-69 years of age. The group with over 75 years had the least people

```


```{r}
# Gender
ggplot(df, aes(D1)) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),fill="blue", color="black") + 
  scale_y_continuous(labels=scales::percent) +
  labs(y = "Percent", fill="day") +
  labs(y = "Percent", title = "Gender Distribution in %")+
  theme_classic()
#Females are slightly higher than males in the survey. 

```

```{r}
# Education
ggplot(df, aes(EDUCATION, fill=EDUCATION)) + 
  geom_bar(aes(y = (..count..)/sum(..count..))) + 
  scale_y_continuous(labels=scales::percent) +
  labs(y = "Percent", title = "Education Distribution in %")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, hjust=1))+
  theme(
    # axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )
# most the people who took part in the survey have attained secondary education.

```

```{r}
#Income 
ggplot(df, aes(INCOME, fill= INCOME)) + 
  geom_bar(aes(y = (..count..)/sum(..count..))) + 
  scale_y_continuous(labels=scales::percent) +
  labs(y = "Percent", title = "Income Distribution in %")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, hjust=1))+
  theme(
    # axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )

#Majority of the people earn between 1510 and 2500 euros

```

```{r}
#HHSIZE
ggplot(df, aes(factor(HHSIZE))) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),fill="blue", color="black") + 
  scale_y_continuous(labels=scales::percent) +
  labs(y = "Percent", title = "Household size",
       x="Household size")+
  theme_classic()

#majority of the households have atmost 2 people per household.
```

```{r}
#Activity status
ggplot(df, aes(factor(D6_1), fill=factor(D6_1))) + 
  geom_bar(aes(y = (..count..)/sum(..count..))) + 
  scale_y_continuous(labels=scales::percent) +
  labs(y = "Percent", title = "Activity status",
       x="Status",fill="Activity")+
  theme_classic()+
  theme(
    # axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )

#Almost 50% of the people are employees. 
```

```{r}
#DEPCHILDREN
ggplot(df, aes(factor(DEPCHILDREN))) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),fill="blue", color="black") + 
  scale_y_continuous(labels=scales::percent) +
  labs(y = "Percent", title = "Number of children or economically dependent",
       x="DEPCHILDREN")+
  theme_classic()

#Over 40% of the participants (majority) do not have dependents.
```

```{r}
#Country
ggplot(df, aes(COUNTRY)) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),fill="blue", color="black") + 
  scale_y_continuous(labels=scales::percent) +
  labs(y = "Percent", title = "Country Distribution in %")+
  theme_classic()

#Most of the participants are from france followed by italy and spain comes in at third position

```


# Pop holding Bundles of payment instruments in percentage

```{r}
POS<- space%>%
  select(QQ1A_1,,QQ1A_2,QQ1A_3,QQ1D)%>%
  mutate(QQ1D= case_when(
    QQ1D==1~	"Yes, it is available for me",
    QQ1D==2~	"No, it is not available for me",
    QQ1D==3~	"heard aboutservice, not sure if available",
    QQ1D==4~	"I have not heard about this service",
    QQ1D==999999~	"Don't know"
    
  ))

Bundles<-count(POS,QQ1A_1,QQ1A_2, QQ1A_3,QQ1D ) %>% ungroup()%>%
  mutate(n= round((n/sum(n))*100,2))%>%
  arrange(desc(n))%>%
  mutate(n= paste0(n," %"))%>%
  head(15)

names(Bundles)<- c("account","crdit.dbit",
                   "crypto", "instnt",
                   "Pop")
kable(Bundles, align = "l")

```

The table presents the distribution of people holding specific payment instruments based on their access or awareness of various payment services. The columns represent different conditions: "account" (whether they have an account), "credit/debit" (whether they have a credit/debit card), "crypto" (whether they have access to cryptocurrency), "instant" (whether they have access to instant payment services), and "Pop" (the percentage of respondents falling into each category). For example, 39.36% of respondents have an account, hold a credit/debit card, and have access to instant payment services, while 14.05% have the same but are uncertain if instant payment is available to them. This table provides insights into the intersections of various payment methods and respondents' access or awareness of these methods, helping to understand the usage patterns and familiarity with different payment instruments among the surveyed population.

The above anlysis haave been broken down by various demographic variables as shwon below. 

# Pop holding Bundles of payment instruments in percentage by Age

```{r}
#### Age

POS<- df%>%
  select(QQ1A_1,,QQ1A_2,QQ1A_3,QQ1D, AGE)%>%
  mutate(QQ1D= case_when(
    QQ1D==1~	"Yes, it is available for me",
    QQ1D==2~	"No, it is not available for me",
    QQ1D==3~	"heard aboutservice, not sure if available",
    QQ1D==4~	"I have not heard about this service",
    QQ1D==999999~	"Don't know"
    
  ))

Bundles<-count(POS,QQ1A_1,QQ1A_2, QQ1A_3,QQ1D ,AGE) %>% ungroup()%>%
  mutate(n= round((n/sum(n))*100,2))%>%
  arrange(desc(n))%>%
  mutate(n= paste0(n," %"))%>%
  head(15)

names(Bundles)<- c("account","crdit.dbit",
                   "crypto", "instnt","AGE",
                   "Pop")

kable(Bundles, align = "l")

```

# Pop holding Bundles of payment instruments in percentage by education

```{r}
#Education 
POS<- df%>%
  select(QQ1A_1,,QQ1A_2,QQ1A_3,QQ1D, EDUCATION)%>%
  mutate(QQ1D= case_when(
    QQ1D==1~	"Yes, it is available for me",
    QQ1D==2~	"No, it is not available for me",
    QQ1D==3~	"heard aboutservice, not sure if available",
    QQ1D==4~	"I have not heard about this service",
    QQ1D==999999~	"Don't know"

  ))

Bundles<-count(POS,QQ1A_1,QQ1A_2, QQ1A_3,QQ1D ,EDUCATION) %>% ungroup()%>%
  mutate(n= round((n/sum(n))*100,2))%>%
  arrange(desc(n))%>%
  mutate(n= paste0(n," %"))%>%
  head(15)

names(Bundles)<- c("account","crdit.dbit",
                   "crypto", "instnt","EDUCATION",
                   "Pop")
kable(Bundles,align = "l")
```

# Pop holding Bundles of payment instruments in percentage by Activity status

```{r}
## Activity Status
POS<- df%>%
  select(QQ1A_1,,QQ1A_2,QQ1A_3,QQ1D, D6_1)%>%
  mutate(QQ1D= case_when(
    QQ1D==1~	"Yes, it is available for me",
    QQ1D==2~	"No, it is not available for me",
    QQ1D==3~	"heard aboutservice, not sure if available",
    QQ1D==4~	"I have not heard about this service",
    QQ1D==999999~	"Don't know"
    
  ))

Bundles<-count(POS,QQ1A_1,QQ1A_2, QQ1A_3,QQ1D ,D6_1) %>% ungroup()%>%
  mutate(n= round((n/sum(n))*100,2))%>%
  arrange(desc(n))%>%
  mutate(n= paste0(n," %"))%>%
  head(15)

names(Bundles)<- c("account","crdit.dbit",
                   "crypto", "instnt","Activity",
                   "Pop")
kable(Bundles, align = "l")
```

# Pop holding Bundles of payment instruments in percentage by employment status

```{r}

## Employment status
POS<- df%>%
  select(QQ1A_1,,QQ1A_2,QQ1A_3,QQ1D, D6_2A)%>%
  mutate(QQ1D= case_when(
    QQ1D==1~	"Yes, it is available for me",
    QQ1D==2~	"No, it is not available for me",
    QQ1D==3~	"heard aboutservice, not sure if available",
    QQ1D==4~	"I have not heard about this service",
    QQ1D==999999~	"Don't know"
    
  ))

Bundles<-count(POS,QQ1A_1,QQ1A_2, QQ1A_3,QQ1D ,D6_2A) %>% ungroup()%>%
  mutate(n= round((n/sum(n))*100,2))%>%
  arrange(desc(n))%>%
  mutate(n= paste0(n," %"))%>%
  head(15)

names(Bundles)<- c("account","crdit.dbit",
                   "crypto", "instnt","Employment_Status",
                   "Pop")
kable(Bundles, align = "l")

```

# Pop holding Bundles of payment instruments in percentage inactivity status

```{r}
###  Inactivity status
POS<- df%>%
  select(QQ1A_1,,QQ1A_2,QQ1A_3,QQ1D, D6_2B)%>%
  mutate(QQ1D= case_when(
    QQ1D==1~	"Yes, it is available for me",
    QQ1D==2~	"No, it is not available for me",
    QQ1D==3~	"heard aboutservice, not sure if available",
    QQ1D==4~	"I have not heard about this service",
    QQ1D==999999~	"Don't know"
    
  ))

Bundles<-count(POS,QQ1A_1,QQ1A_2, QQ1A_3,QQ1D ,D6_2B) %>% ungroup()%>%
  mutate(n= round((n/sum(n))*100,2))%>%
  arrange(desc(n))%>%
  mutate(n= paste0(n," %"))%>%
  head(15)

names(Bundles)<- c("account","crdit.dbit",
                   "crypto", "instnt","Inactivity_Status",
                   "Pop")
kable(Bundles, align = "l")

```

# Pop holding Bundles of payment instruments in percentage by household size

```{r}
###  Household size
POS<- df%>%
  select(QQ1A_1,,QQ1A_2,QQ1A_3,QQ1D, HHSIZE)%>%
  mutate(QQ1D= case_when(
    QQ1D==1~	"Yes, it is available for me",
    QQ1D==2~	"No, it is not available for me",
    QQ1D==3~	"heard aboutservice, not sure if available",
    QQ1D==4~	"I have not heard about this service",
    QQ1D==999999~	"Don't know"
    
  ))

Bundles<-count(POS,QQ1A_1,QQ1A_2, QQ1A_3,QQ1D ,HHSIZE) %>% ungroup()%>%
  mutate(n= round((n/sum(n))*100,2))%>%
  arrange(desc(n))%>%
  mutate(n= paste0(n," %"))%>%
  head(15)

names(Bundles)<- c("account","crdit.dbit",
                   "crypto", "instnt","HHSIZE",
                   "Pop")
kable(Bundles, align = "l")
```

# Pop holding Bundles of payment instruments in percentage by income

```{r}
### INCOME
POS<- df%>%
  select(QQ1A_1,,QQ1A_2,QQ1A_3,QQ1D, INCOME)%>%
  mutate(QQ1D= case_when(
    QQ1D==1~	"Yes, it is available for me",
    QQ1D==2~	"No, it is not available for me",
    QQ1D==3~	"heard aboutservice, not sure if available",
    QQ1D==4~	"I have not heard about this service",
    QQ1D==999999~	"Don't know"
    
  ))

Bundles<-count(POS,QQ1A_1,QQ1A_2, QQ1A_3,QQ1D ,INCOME) %>% ungroup()%>%
  mutate(n= round((n/sum(n))*100,2))%>%
  arrange(desc(n))%>%
  mutate(n= paste0(n," %"))%>%
  head(15)

names(Bundles)<- c("account","crdit.dbit",
                   "crypto", "instnt","INCOME",
                   "Pop")
kable(Bundles, align = 'l')

```

# Pop holding Bundles of payment instruments in percentage country

```{r}
### country 

POS<- df%>%
  select(QQ1A_1,,QQ1A_2,QQ1A_3,QQ1D, COUNTRY)

for(country in unique(POS$COUNTRY)){
  dd<- POS%>%
    filter(COUNTRY %in% country)
  
  Bundles2<-count(dd,QQ1A_1,QQ1A_2, QQ1A_3,QQ1D ,COUNTRY) %>% ungroup()%>%
    mutate(n= round((n/sum(n))*100,2))%>%
    arrange(desc(n))%>%
    mutate(n= paste0(n," %"))%>%
    head(15)
  
  names(Bundles2)<- c("account","crdit.dbit",
                     "crypto", "instnt","COUNTRY",
                     "Pop")
  print(kable(Bundles2, align = 'l', caption = paste0(country,"'s Population Holdings of the Top 15 Bundles of Payment Instruments")))
  
}

```

# Average spending on various commodities using different instruments

```{r}
# online payment

online<- space%>%
  select(starts_with(c("QB1_","QB3_", "QB4_")))#,QB3_n,QB4_n)
online[online>100 & !is.na(online)]<- NA

df_1<- online%>%
  select(ends_with("_1"))%>%
  mutate(QB1_1= case_when(
    QB1_1==1~	"Clothes_sportswear",
    QB1_1==2~	"Electronic_goods",
    QB1_1==3~	"Food_daily.supplies",
    QB1_1==4~	"Medicine",
    QB1_1==5~	"entertainment",
    QB1_1==6~	"Donations",
    QB1_1==7~	"Accommodation",
    QB1_1==8~	"Furniture",
    QB1_1==9~	"Tickets",
    QB1_1==10~	"Luxury_goods",
    QB1_1==11~	"Financial_products",
    QB1_1==12~	"Household_related",
    QB1_1==13~	"Other",
    QB1_1==999999~	"Don't know"

  ),
  QB4_1= case_when(
    QB4_1==1~"Card",
    QB4_1==3~"PayPal",
    QB4_1==4~	"Other.online",
    QB4_1==5~	"Direct",
    QB4_1==6~	"Credit",
    QB4_1==8~	"Loyalty",
    QB4_1==10~	"Crypto-assets",
    QB4_1==11~	"Other",
    QB4_1==999999~	"Don't know"

  ))

df_1.clean<- df_1%>%
  drop_na()

grouped_1<-df_1.clean%>%
  group_by(QB4_1, QB1_1)%>%
  summarise(mean= mean(QB3_1, na.rm = T))

dd<-pivot_wider(grouped_1, names_from = QB4_1, 
            values_from = mean)
kable(dd, digits = 2,  align = "l")
```

The table above shows the average spending on various commodities using different instruments. For example the average spending on on donations using credit card is 26.31
This comprison has also be broken down by demographics and country. 

# Compare average spending on various commodities using different instruments by AGE

```{r message=FALSE}
#compare by demographic
df_3<- data.frame(df_1, AGE= df$AGE)%>%
  drop_na()

for(age in unique(df_3$AGE)){
  df_3.sub<- df_3%>%
    filter(AGE== age)
  grouped_3<-df_3.sub%>%
    group_by(QB4_1, QB1_1)%>%
    summarise(mean= mean(QB3_1, na.rm = T),)
  
  dd_3<-pivot_wider(grouped_3, names_from = QB4_1, 
                    values_from = mean)
  print(kable(dd_3, digits = 2, align = "l", 
              caption=paste0(age, "'s online Payment")))
  
}
```


# compare average spending on various commodities using different instruments by country 

```{r, message=FALSE}
#compare by country 

df_2<- data.frame(df_1, Country= space$COUNTRY)%>%
  drop_na()



for( country in unique(df_2$Country)){
  df_2.sub<- df_2%>%
    filter(Country == country)
  grouped_2<-df_2.sub%>%
    group_by(QB4_1, QB1_1)%>%
    summarise(mean= mean(QB3_1, na.rm = T))
  
  dd_2<-pivot_wider(grouped_2, names_from = QB4_1, 
                  values_from = mean)
  print(kable(dd_2,digits = 2,
              align = "l",
              caption=paste0(country, "'s online Payment")))
}
```



# Adoption Rate 

```{r}
#One chart for adoption Rate 

adoption<- space%>%
  select(QQ1A_1,QQ1A_2, QQ1A_3, QQ1A_4, QQ1A_5)
names(adoption)<- c("Cash", "Credit.debit","Crypto","None","Not.Sure")

ratios <- apply(data.matrix(adoption)[,], 2, function(x) length(which(x == 1)) / nrow(adoption))

ff<- data.frame(#instruments=c("Cash", "Credit.debit","Crypto","None","Not.Sure"),
                Adoption.Rate= ratios)
kable(ff, align = "l", caption = "Adoption Rate")
```

The table above shows how people have adopted various instruments. over 89 % of the population have a payment account. The comparison have also been broken down by demographics as shown below. 

# comapare adoption by country

```{r}
# by country 
adoption<- space%>%
  select(QQ1A_1,QQ1A_2, QQ1A_3, QQ1A_4, QQ1A_5, COUNTRY)

for( country in unique(adoption$COUNTRY)){
  dat<- adoption%>%
    filter(COUNTRY== country)%>%
    select(-COUNTRY)
  names(dat)<- c("Payment.account", "Credit.debit","Crypto","None","Not.Sure")
  ratios <- apply(data.matrix(dat)[,], 2, function(x) length(which(x == 1)) / nrow(dat))
  
  ff<- data.frame(#instruments=c("Cash", "Credit.debit","Crypto","None","Not.Sure"),
    Adoption.Rate= ratios)
  print(kable(ff, align = "l", caption=paste0(country, "'s Adoption Rate")))
  
}
```


# comapare adoption by AGE

```{r}
# by country 
adoption<- space%>%
  select(QQ1A_1,QQ1A_2, QQ1A_3, QQ1A_4, QQ1A_5)
adoption$AGE<- df$AGE

for(age in unique(adoption$AGE)){
  dat<- adoption%>%
    filter(AGE== age)%>%
    select(-AGE)
  names(dat)<- c("Payment.account", "Credit.debit","Crypto","None","Not.Sure")
  ratios <- apply(data.matrix(dat)[,], 2, function(x) length(which(x == 1)) / nrow(dat))
  
  ff<- data.frame(#instruments=c("Cash", "Credit.debit","Crypto","None","Not.Sure"),
    Adoption.Rate= ratios)
  print(kable(ff, align = "l", caption=paste0(age, "'s Adoption Rate")))
  
}
```

# comapare adoption by Gender

```{r}
# by country 
adoption<- space%>%
  select(QQ1A_1,QQ1A_2, QQ1A_3, QQ1A_4, QQ1A_5)
adoption$D1<- df$D1

for(d1 in unique(adoption$D1)){
  dat<- adoption%>%
    filter(D1== d1)%>%
    select(-D1)%>%
    drop_na()
  names(dat)<- c("Payment.account", "Credit.debit","Crypto","None","Not.Sure")
  ratios <- apply(data.matrix(dat)[,], 2, function(x) length(which(x == 1)) / nrow(dat))
  
  ff<- data.frame(Adoption.Rate= ratios)
  print(kable(ff, align = "l", caption=paste0(d1, "'s Adoption Rate")))
  
}
```

# comapare adoption by Activity 

```{r}
# by country 
adoption<- space%>%
  select(QQ1A_1,QQ1A_2, QQ1A_3, QQ1A_4, QQ1A_5)
adoption$D6_1<- df$D6_1

for(d6_1 in unique(adoption$D6_1)){
  dat<- adoption%>%
    filter(D6_1== d6_1)%>%
    select(-D6_1)%>%
    drop_na()
  names(dat)<- c("Payment.account", "Credit.debit","Crypto","None","Not.Sure")
  ratios <- apply(data.matrix(dat)[,], 2, function(x) length(which(x == 1)) / nrow(dat))
  
  ff<- data.frame(Adoption.Rate= ratios)
  print(kable(ff, align = "l", caption=paste0(d6_1, "'s Adoption Rate")))
  
}
```

# comapare adoption by EDUCutation

```{r}
# by country 
adoption<- space%>%
  select(QQ1A_1,QQ1A_2, QQ1A_3, QQ1A_4, QQ1A_5)
adoption$EDUCATION<- df$EDUCATION

for(edu in unique(adoption$EDUCATION)){
  dat<- adoption%>%
    filter(EDUCATION== edu)%>%
    select(-EDUCATION)
  names(dat)<- c("Payment.account", "Credit.debit","Crypto","None","Not.Sure")
  ratios <- apply(data.matrix(dat)[,], 2, function(x) length(which(x == 1)) / nrow(dat))
  
  ff<- data.frame(#instruments=c("Cash", "Credit.debit","Crypto","None","Not.Sure"),
    Adoption.Rate= ratios)
  print(kable(ff, align = "l", caption=paste0(edu, "'s Adoption Rate")))
  
}
```

# comapare adoption by INCOME

```{r}
# by country 
adoption<- space%>%
  select(QQ1A_1,QQ1A_2, QQ1A_3, QQ1A_4, QQ1A_5)
adoption$INCOME<- df$INCOME

for(income in unique(adoption$INCOME)){
  dat<- adoption%>%
    filter(INCOME== income)%>%
    select(-INCOME)
  names(dat)<- c("Payment.account", "Credit.debit","Crypto","None","Not.Sure")
  ratios <- apply(data.matrix(dat)[,], 2, function(x) length(which(x == 1)) / nrow(dat))
  
  ff<- data.frame(#instruments=c("Cash", "Credit.debit","Crypto","None","Not.Sure"),
    Adoption.Rate= ratios)
  print(kable(ff, align = "l", caption=paste0(income, "'s Adoption Rate")))
  
}
```

# comapare adoption by HHSIZE

```{r}
# by country 
adoption<- space%>%
  select(QQ1A_1,QQ1A_2, QQ1A_3, QQ1A_4, QQ1A_5)
adoption$HHSIZE<- df$HHSIZE

for(hhsize in unique(adoption$HHSIZE)){
  dat<- adoption%>%
    filter(HHSIZE== hhsize)%>%
    select(-HHSIZE)
  names(dat)<- c("Payment.account", "Credit.debit","Crypto","None","Not.Sure")
  ratios <- apply(data.matrix(dat)[,], 2, function(x) length(which(x == 1)) / nrow(dat))
  
  ff<- data.frame(#instruments=c("Cash", "Credit.debit","Crypto","None","Not.Sure"),
    Adoption.Rate= ratios)
  print(kable(ff, align = "l", caption=paste0(hhsize, "'s Adoption Rate")))
  
}
```


# Cash advantage 

```{r}
#cash advantage
cash.advg<- space%>%
  select(QQ13A_1,QQ13A_2,QQ13A_3,QQ13A_4,QQ13A_5,
         QQ13A_6, QQ13A_7, QQ13A_8,QQ13A_9,QQ13A_10,QQ13A_11)
names(cash.advg)<- c("cash.acceptance", "cash.faster","cash.privacy","cash.easier",
                     "cash.safer","immediately_settled","aware_spending",
                     "other_advantage","do_not_use_cash","no_advantage",
                     "dont_know")
ratios <- apply(data.matrix(cash.advg)[,], 2, function(x) length(which(x == 1)) / nrow(cash.advg))

cash.advg.rate<- data.frame(#instruments=c("Cash", "Credit.debit","Crypto","None","Not.Sure"),
  Advantage.Rating= ratios)
kable(cash.advg.rate, align = "l", caption = "Cash advatange ratio")
```

The table above the ration of people who believe that cash has advantage for given reason. e.g. 29.12% of the population believe that cash is advantageous since it is easily accepted. 

We will break down the same comparison suing different demographics.

# Age Comaprios for Cash Advantage

```{r}
cash.advg.age<- data.frame(cash.advg, AGE= df$AGE)

for(age in unique(cash.advg.age$AGE)){
  dd<- cash.advg.age%>%
    filter(AGE==age)%>%
    drop_na()
  
  ratios <- apply(data.matrix(dd)[,], 2, function(x) length(which(x == 1)) / nrow(dd))
  
  print(kable(data.frame(Advantage.Rating= ratios), align = "l", caption =paste0(age, "'s Cash advatange ratio")))
}
```

#Gender comariosn for cash advantage

```{r}
cash.advg.D1<- data.frame(cash.advg, D1= df$D1)%>%
  drop_na()

for(d1 in unique(cash.advg.D1$D1)){
  dd<- cash.advg.D1%>%
    filter(D1==d1)%>%
    drop_na()
  
  ratios <- apply(data.matrix(dd)[,], 2, function(x) length(which(x == 1)) / nrow(dd))
  
  print(kable(data.frame(Advantage.Rating= ratios), align = "l", caption =paste0(d1, "'s Cash advatange ratio")))
  
}
```

# Activity Status comariosn for cash advantage

```{r}
cash.advg.D6_1<- data.frame(cash.advg, D6_1= df$D6_1)%>%
  drop_na()

for(d6_1 in unique(cash.advg.D6_1$D6_1)){
  dd<- cash.advg.D6_1%>%
    filter(D6_1==d6_1)%>%
    select(-D6_1)%>%
    drop_na()
  
  ratios <- apply(data.matrix(dd)[,], 2, function(x) length(which(x == 1)) / nrow(dd))
  
  print(kable(data.frame(Advantage.Rating= ratios), align = "l", caption =paste0(d6_1, "'s Cash advatange ratio")))
  
}
```

# Education comaprion for cash advantange 

```{r}
cash.advg.edu<- data.frame(cash.advg, EDU= df$EDUCATION)

for(edu in unique(cash.advg.edu$EDU)){
  dd<- cash.advg.edu%>%
    filter(EDU==edu)%>%
    drop_na()
  
  ratios <- apply(data.matrix(dd)[,], 2, function(x) length(which(x == 1)) / nrow(dd))
  
  print(kable(data.frame(Advantage.Rating= ratios), align = "l", caption =paste0(edu, "'s Cash advatange ratio")))
}
```

# Income comaprison for cash advantage 

```{r}
cash.advg.income<- data.frame(cash.advg, INCOME= df$INCOME)%>%
  drop_na()

for(income in unique(cash.advg.income$INCOME)){
  dd<- cash.advg.income%>%
    filter(INCOME==income)%>%
    drop_na()
  
  ratios <- apply(data.matrix(dd)[,], 2, function(x) length(which(x == 1)) / nrow(dd))
  
  print(kable(data.frame(Advantage.Rating= ratios), align = "l", caption =paste0(income, "'s Cash advatange ratio")))
  
}
```

# HHsize cash advantage comparison

```{r}
cash.advg.hhsize<- data.frame(cash.advg, HHSIZE= df$HHSIZE)

for(hhsize in unique(cash.advg.hhsize$HHSIZE)){
  dd<- cash.advg.hhsize%>%
    filter(HHSIZE==hhsize)%>%
    drop_na()
  
  ratios <- apply(data.matrix(dd)[,], 2, function(x) length(which(x == 1)) / nrow(dd))
  
  print(kable(data.frame(Advantage.Rating= ratios), align = "l", caption =paste0(hhsize, "'s Cash advatange ratio")))
  
}
```


# Card Advantage comparison

```{r}
#card advantages

card.advg<- space%>%
select(QQ13B_1,QQ13B_2,QQ13B_3,QQ13B_4,QQ13B_5,
       QQ13B_6, QQ13B_7, QQ13B_8,QQ13B_9,QQ13B_10)
names(card.advg)<- c("card.acceptance", "card.faster","card.easier",
                "card.safer","no_worry_carrying_cash","aware_spending",
                "other_advantage","no_advantage","do_not_use_card",
                "dont_know")

ratios <- apply(data.matrix(card.advg)[,], 2, function(x) length(which(x == 1)) / nrow(card.advg))

card.advg.rate<- data.frame(#instruments=c("Cash", "Credit.debit","Crypto","None","Not.Sure"),
  Advantage.Rating= ratios)

kable(card.advg.rate, align = "l", caption = "Card advatange ratio")
```

Similar to the cash advantage table, the table displays the % of population who think card has advantages for various reasons. inthis case, 42.97% of the people suggested that card has advantages since it is faster to use. We will do a similar compariosn by breaking it down suing demographics. 

#  Age Comaprios for Card Advantage

```{r}
card.advg.age<- data.frame(card.advg, AGE= df$AGE)

for(age in unique(card.advg.age$AGE)){
  dd<- card.advg.age%>%
    filter(AGE==age)%>%
    drop_na()

  ratios <- apply(data.matrix(dd)[,], 2, function(x) length(which(x == 1)) / nrow(dd))

  print(kable(data.frame(Advantage.Rating= ratios), align = "l", caption =paste0(age, "'s Card advatange ratio")))
}
```


#Gender compariosn for card advantage

```{r}
card.advg.D1<- data.frame(card.advg, D1= df$D1)%>%
  drop_na()

for(d1 in unique(card.advg.D1$D1)){
  dd<- card.advg.D1%>%
    filter(D1==d1)%>%
    drop_na()
  
  ratios <- apply(data.matrix(dd)[,], 2, function(x) length(which(x == 1)) / nrow(dd))
  
  print(kable(data.frame(Advantage.Rating= ratios), align = "l", caption =paste0(d1, "'s Card advatange ratio")))
  
}
```

# Activity Status compariosn for card advantage

```{r}
card.advg.D6_1<- data.frame(card.advg, D6_1= df$D6_1)%>%
  drop_na()

for(d6_1 in unique(card.advg.D6_1$D6_1)){
  dd<- card.advg.D6_1%>%
    filter(D6_1==d6_1)%>%
    drop_na()
  
  ratios <- apply(data.matrix(dd)[,], 2, function(x) length(which(x == 1)) / nrow(dd))
  
  print(kable(data.frame(Advantage.Rating= ratios), align = "l", caption =paste0(d6_1, "'s Card advatange ratio")))
  
}
```

# Education comaprion for card advantange 

```{r}
card.advg.edu<- data.frame(card.advg, EDU= df$EDUCATION)

for(edu in unique(card.advg.edu$EDU)){
  dd<- card.advg.edu%>%
    filter(EDU==edu)%>%
    drop_na()
  
  ratios <- apply(data.matrix(dd)[,], 2, function(x) length(which(x == 1)) / nrow(dd))
  
  print(kable(data.frame(Advantage.Rating= ratios), align = "l", caption =paste0(edu, "'s Card advatange ratio")))
}
```

# Income comaprison for card advantage 

```{r}
card.advg.income<- data.frame(card.advg, INCOME= df$INCOME)%>%
  drop_na()

for(income in unique(card.advg.income$INCOME)){
  dd<- card.advg.income%>%
    filter(INCOME==income)%>%
    drop_na()
  
  ratios <- apply(data.matrix(dd)[,], 2, function(x) length(which(x == 1)) / nrow(dd))
  
  print(kable(data.frame(Advantage.Rating= ratios), align = "l", caption =paste0(income, "'s Card advatange ratio")))
  
}
```

# HHsize card advantage comparison

```{r}
card.advg.hhsize<- data.frame(card.advg, HHSIZE= df$HHSIZE)

for(hhsize in unique(card.advg.hhsize$HHSIZE)){
  dd<- card.advg.hhsize%>%
    filter(HHSIZE==hhsize)%>%
    drop_na()
  
  ratios <- apply(data.matrix(dd)[,], 2, function(x) length(which(x == 1)) / nrow(dd))
  
  print(kable(data.frame(Advantage.Rating= ratios), align = "l", caption =paste0(hhsize, "'s Card advatange ratio")))
  
}
```

# Covid19 comaprison 

```{r}
Covid<- space%>%
  select(QQ19A)%>%
  mutate(QQ19A=case_when(
    QQ19A==1~	"Much more often",
    QQ19A==2~	"Somewhat more often",
    QQ19A==3~	"The same as before",
    QQ19A==4~	"Somewhat less often",
    QQ19A==5~	"Much less often",
    QQ19A==999999~	"Don't know",

  ))

pp<-prop.table(table(Covid$QQ19A))

covid_dist<- data.frame( Use.of.cash= pp)

kable(covid_dist, align = 'l', caption = "are you using cash instead of non-cash payment methods more")
```

The table shows a representation of how use of cash has changed before and during covid 19. Over 52.66% of the population continued to use cash in the same frequecy as they did before covid 19. 
The same analysis above has been broken down by demographic

# Comapare cash frequecy use during and before covid 19 by demographics
#####

#  Age Comaprios for Caash frequecy use during and before covid 19

```{r}
Covid.age<- data.frame(Covid, AGE= df$AGE)

for(age in unique(Covid.age$AGE)){
  dd<- Covid.age%>%
    filter(AGE==age)%>%
    select(-AGE)%>%
    drop_na()
  
  pp<-prop.table(table(dd$QQ19A))

  covid_dist<- data.frame( Use.of.cash= pp)

  print(kable(covid_dist, align = "l", caption =paste0(age, "'s cash freq ratio")))
}
```

# Gender Comaprios for Caash frequecy use during and before covid 19

```{r}
Covid.d1<- data.frame(Covid, D1= df$D1)

for(d1 in unique(Covid.d1$D1)){
  dd<- Covid.d1%>%
    filter(D1==d1)%>%
    select(-D1)%>%
    drop_na()
  
  pp<-prop.table(table(dd$QQ19A))

  covid_dist<- data.frame( Use.of.cash= pp)

  print(kable(covid_dist, align = "l", caption =paste0(d1, "'s cash freq ratio")))
}
```

#  Activity Status Comaprios for Caash frequecy use during and before covid 19

```{r}
Covid.D6_1<- data.frame(Covid, D6_1= df$D6_1)

for(d6_1 in unique(Covid.D6_1$D6_1)){
  dd<- Covid.D6_1%>%
    filter(D6_1==d6_1)%>%
    select(-D6_1)%>%
    drop_na()
  
  pp<-prop.table(table(dd$QQ19A))

  covid_dist<- data.frame( Use.of.cash= pp)

  print(kable(covid_dist, align = "l", caption =paste0(d6_1, "'s cash freq ratio")))
}
```

#  EDUCATION Comaprios for Caash frequecy use during and before covid 19

```{r}
Covid.edu<- data.frame(Covid, EDUCATION= df$EDUCATION)

for(edu in unique(Covid.edu$EDUCATION)){
  dd<- Covid.edu%>%
    filter(EDUCATION==edu)%>%
    drop_na()
  
  pp<-prop.table(table(dd$QQ19A))

  covid_dist<- data.frame( Use.of.cash= pp)

  print(kable(covid_dist, align = "l", caption =paste0(edu, "'s cash freq ratio")))
}
```



#  HHSIZE Comaprios for Caash frequecy use during and before covid 19

```{r}
Covid.hhsize<- data.frame(Covid, HHSIZE= df$HHSIZE)

for(hhsize in unique(Covid.hhsize$HHSIZE)){
  dd<- Covid.hhsize%>%
    filter(HHSIZE==hhsize)%>%
    drop_na()
  
  pp<-prop.table(table(dd$QQ19A))

  covid_dist<- data.frame( Use.of.cash= pp)

  print(kable(covid_dist, align = "l", caption =paste0(hhsize, "'s cash freq ratio")))
}
```

#  INCOME Comaprios for Caash frequecy use during and before covid 19

```{r}
Covid.income<- data.frame(Covid, INCOME= df$INCOME)

for(income in unique(Covid.income$INCOME)){
  dd<- Covid.income%>%
    filter(INCOME==income)%>%
    drop_na()
  
  pp<-prop.table(table(dd$QQ19A))

  covid_dist<- data.frame( Use.of.cash= pp)

  print(kable(covid_dist, align = "l", caption =paste0(income, "'s cash freq ratio")))
}
```

# Less cash table
```{r}
#Less cash 
less.cash<- space%>%
  select(starts_with("Q19C_"))
names(less.cash)<- c('difficult.withdraw','fear.virus',
                     'cash.not.accepted','advice.not.use.cash',
                     'gover.recomm', 'electronic.better',
                     'new.means','other.reason',
                     'dont.know')
less.cash2<- less.cash
less.cash<- na.omit(less.cash)
ratios <- apply(data.matrix(less.cash)[,], 2, function(x) length(which(x == 1)) / nrow(less.cash))

df.less<- data.frame( Advantage.Rating= ratios)
kable(df.less, align = "l", caption =paste0("Less Cash", ""))
```

The table shows the percentage in each caterory as to why people used less cash during covid 19. .eg 58.51% of people used less cash since electronic method was much better. 
Now lets break the analysis by demographic


#AGE Comaprios for Caash frequecy use during and before covid 19

```{r}
Covid.age<- data.frame(less.cash2, AGE= df$AGE)

for(age in unique(Covid.age$AGE)){
  dd<- Covid.age%>%
    filter(AGE==age)%>%
    select(-AGE)%>%
    drop_na()
  
ratios <- apply(data.matrix(dd)[,], 2, function(x) length(which(x == 1)) / nrow(dd))

df.less<- data.frame( Advantage.Rating= ratios)
print(kable(df.less, align = "l", caption =paste0(age, "'s less cash freq ratio")))
}
```

# income Comaprios for Caash frequecy use during and before covid 19

```{r}
Covid.income<- data.frame(less.cash2, INCOME= df$INCOME)

for(income in unique(Covid.income$INCOME)){
  dd<- Covid.income%>%
    filter(INCOME==income)%>%
    select(-INCOME)%>%
    drop_na()
  
ratios <- apply(data.matrix(dd)[,], 2, function(x) length(which(x == 1)) / nrow(dd))

df.less<- data.frame( Advantage.Rating= ratios)
print(kable(df.less, align = "l", caption =paste0(income, "'s less cash freq ratio")))
}
```

# Gender Comaprios for Caash frequecy use during and before covid 19

```{r}
Covid.d1<- data.frame(less.cash2, D1= df$D1)

for(d1 in unique(Covid.d1$D1)){
  dd<- Covid.d1%>%
    filter(D1==d1)%>%
    select(-D1)%>%
    drop_na()
  
ratios <- apply(data.matrix(dd)[,], 2, function(x) length(which(x == 1)) / nrow(dd))

df.less<- data.frame( Advantage.Rating= ratios)
print(kable(df.less, align = "l", caption =paste0(d1, "'s less cash freq ratio")))
}
```

# Education Comaprios for Caash frequecy use during and before covid 19

```{r}
Covid.edu<- data.frame(less.cash2, EDUCATION= df$EDUCATION)

for(edu in unique(Covid.edu$EDUCATION)){
  dd<- Covid.edu%>%
    filter(EDUCATION==edu)%>%
    select(-EDUCATION)%>%
    drop_na()
  
ratios <- apply(data.matrix(dd)[,], 2, function(x) length(which(x == 1)) / nrow(dd))

df.less<- data.frame( Advantage.Rating= ratios)
print(kable(df.less, align = "l", caption =paste0(edu, "'s less cash freq ratio")))
}
```

# Activity status Comaprios for Caash frequecy use during and before covid 19

```{r}
Covid.d6_1<- data.frame(less.cash2, D6_1= df$D6_1)

for(d6_1 in unique(Covid.edu$EDUCATION)){
  dd<- Covid.d6_1%>%
    filter(D6_1==d6_1)%>%
    select(-D6_1)%>%
    drop_na()
  
ratios <- apply(data.matrix(dd)[,], 2, function(x) length(which(x == 1)) / nrow(dd))

df.less<- data.frame( Advantage.Rating= ratios)
print(kable(df.less, align = "l", caption =paste0(d6_1, "'s less cash freq ratio")))
}
```

# HHSIZE Comaprios for Caash frequecy use during and before covid 19

```{r}
Covid.hhsize<- data.frame(less.cash2, HHSIZE= df$HHSIZE)

for(hhsize in unique(Covid.hhsize$HHSIZE)){
  dd<- Covid.hhsize%>%
    filter(HHSIZE== hhsize)%>%
    select(-HHSIZE)%>%
    drop_na()
  
ratios <- apply(data.matrix(dd)[,], 2, function(x) length(which(x == 1)) / nrow(dd))

df.less<- data.frame( Advantage.Rating= ratios)
print(kable(df.less, align = "l", caption =paste0(hhsize, "'s less cash freq ratio")))
}
```


## Table 5
```{r}
card.advg<- space%>%
select(QQ13B_1,QQ13B_2,QQ13B_3,QQ13B_4,QQ13B_5,
       QQ13B_6, QQ13B_7, QQ13B_8,QQ13B_9,QQ13B_10)
names(card.advg)<- c("card.acceptance", "card.faster","card.easier",
                "card.safer","no_worry_carrying_cash","aware_spending",
                "other_advantage","no_advantage","do_not_use_card",
                "dont_know")
#Covariance matrix 
card.advg2<- na.omit(card.advg)
```

```{r fig.cap ="Covariance Matrix for Ratings of credit Cards",fig.width=12, fig.height=8}
corrplot(cov(card.advg2), method = 'number',col = COL2('RdYlBu', 2),
         type = 'lower', tl.col='black')
```
Covariance measures the degree to which two variables change together; a positive covariance indicates that when one variable increases, the other tends to increase as well, while a negative covariance suggests that when one variable increases, the other tends to decrease. Here, for instance, the covariance between "card.acceptance" and "card.faster" is 0.1699, implying a positive relationship where higher acceptance of cards is associated with a faster card transaction experience. Conversely, the negative covariance between "card.acceptance" and "no_worry_carrying_cash" (-0.0124) suggests that as card acceptance increases, the tendency to worry about carrying cash decreases. This table provides insights into how these variables move in relation to each other, but it doesn't standardize for the scales of the variables, making it difficult to compare the strengths of these relationships directly.


```{r}
#by months 
paymethod<- space%>%
  select(QA7A_1, QA7AI_1, QA7AII_1)%>%
  mutate(QA7A_1= case_when(QA7A_1==1~	"Cash",
                           QA7A_1==2~	"Card",
                           QA7A_1==3~	"Mobile phone app",
                           QA7A_1==4~	"Bank cheque",
                           QA7A_1==5~	"Credit transfer",
                          QA7A_1==6~	"Loyalty points",
                          QA7A_1==7~	"Other",
                         # QA7A_1==999999~	"Don't know",
),
QA7AI_1= case_when(
  QA7AI_1==1~"By inserting the card into a terminal",
  QA7AI_1==2~	"Using contactless technology",
  #QA7AI_1==999999	~"Don't know"

),
QA7AII_1=case_when(
  QA7AII_1== 1~	"Using my bank's mobile application",
QA7AII_1==2~	"Using ApplePay",
QA7AII_1==3~	"Using GooglePay",
QA7AII_1==4~	"Other",
QA7AII_1==5~	"Payconiq by Bancontact",
QA7AII_1==6~	"mTasku",
QA7AII_1==8	~"Jiffy",
QA7AII_1==9~	"Swedbank mobila lietotne",
QA7AII_1==10~	"MoQ",
QA7AII_1==11~	"Digicash",
QA7AII_1==12~	"Bank of Valletta",
QA7AII_1==13~	"Bankomatkarte mobil",
QA7AII_1==14~	"MBway",
QA7AII_1==15~	"NLB pay",
QA7AII_1==16~	"MobilePay TB",
QA7AII_1==17~	"MobilePay",
QA7AII_1==18~	"Swedbanki mobiilipank",
QA7AII_1==19~	"Viva",
QA7AII_1==20~	"Samsung Pay",
QA7AII_1==22~	"Satispay",
QA7AII_1==23~	"Citadele mobila aplikacija",
QA7AII_1==24~	"Revolut",
QA7AII_1==25~	"Bluecode",
QA7AII_1==26~	"mDenarnic@",
QA7AII_1==27~	"mBank SK",
QA7AII_1==28~	"Siirto",
QA7AII_1==29~	"Paypal",
QA7AII_1==30~	"Android pay",
QA7AII_1==31~	"SEB mobila lietotne",
QA7AII_1==32~	"kWallet",
QA7AII_1==33~	"Wave2Pay",
QA7AII_1==34~	"VÚB Mobil Banking",
QA7AII_1==35~	"my Alpha wallet",
QA7AII_1==36~	"Lydia",
QA7AII_1==37~	"Mobilly (parking, train tickets)",
QA7AII_1==38~	"ZOIN",
QA7AII_1==39~	"mBills",
QA7AII_1==40~	"i-bank Pay",
QA7AII_1==41~	"Pumpkin",
QA7AII_1==42~	"Paylib",
QA7AII_1==43~	"Pivo",
#QA7AII_1==999999~"	Don't know",
  
))

paymethod1<- paymethod%>%
  drop_na(QA7A_1)
prop.table(table(paymethod1$QA7A_1))%>%
  data.frame()%>%
  arrange(desc(Freq))%>%
  kable(align = "l", col.names = c("Instrument of POS payment","Population"),
        caption = "Instrument of POS payment by population")
```

The table presents the distribution of the population using various methods of point-of-sale (POS) payments. It outlines the proportions of individuals or users utilizing different payment instruments, including cash, cards, mobile phone apps, credit transfers, other methods, loyalty points, and bank cheques. For instance, approximately 59.18% of the population prefers cash as their POS payment method, while 34.79% opt for cards, and a smaller percentage, 3.29%, rely on mobile phone apps. Credit transfers, other methods, loyalty points, and bank cheques are used by 1.30%, 0.85%, 0.32%, and 0.28% of the population, respectively. This table provides valuable insights into the payment preferences within the population, which can be instrumental for businesses and policymakers in tailoring their financial services and strategies to meet the diverse needs of their customer base.

```{r}

paymethod2<- paymethod%>%
  drop_na(QA7AI_1)
prop.table(table(paymethod2$QA7AI_1))%>%
  data.frame()%>%
  arrange(desc(Freq))%>%
  kable(align = "l", col.names = c("Card payment","Population"),
        caption = "Card payment by population")
```

The table illustrates the distribution of card payment methods within a population. It showcases the proportions of individuals utilizing two distinct ways of making payments with their cards. Approximately 64.07% of the population prefers the convenience of contactless technology for their card payments, allowing for quick and secure transactions by tapping the card on a terminal. In contrast, a smaller portion, accounting for 35.93% of the population, opts for the traditional method of card payment by inserting the card into a terminal. This table highlights the growing popularity of contactless payments, which offer speed and ease of use, reflecting a shift in consumer preferences and technology adoption trends within the payment landscape.

```{r}
paymethod3<- paymethod%>%
  drop_na(QA7AII_1)
prop.table(table(paymethod3$QA7AII_1))%>%
  data.frame()%>%
  arrange(desc(Freq))%>%
  kable(align = "l", col.names = c("Mobile payment","Population"),
        caption = "Mobile payment  by population")
```

The table presents the distribution of mobile payment methods within a population, highlighting the preferences of individuals when it comes to making payments using mobile technology. Among the various options, ApplePay stands out as the most popular choice, with approximately 27.31% of the population opting for this mobile payment solution. Following closely is the use of the bank's mobile application, accounting for 26.01%. GooglePay is also a commonly used method, chosen by 17.71% of users. Other mobile payment options, such as MobilePay, MBway, and Samsung Pay, are selected by smaller proportions of the population, ranging from 3.60% to 1.93%. This table reveals the diverse landscape of mobile payment preferences, reflecting the influence of both platform-specific and region-specific solutions, which can provide valuable insights for businesses and financial institutions seeking to cater to their customers' varied needs in the mobile payment sector.


